---
title: "ggpalette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggpalette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggpalette)
library(palmerpenguins)
library(ggplot2)
```

## Overview
In the ggpalette, there are 6 colours in it. They are pink, orange, navy, grey, magenta and green. You can allow ggplot2 to use the colour palette. There are discrete ggplot palettes and continuous colour scale.


### Generate discrete ggplot palettes
 Added with ggplot2 
```{r warning=FALSE}
p1 <- ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color = sex)) +
  geom_point(size = 2) +
  scale_colour_ggpalette_d() +
  theme_bw()
p1
```

Use direction = -1 to reserve the order of the palette
```{r warning=FALSE}
p1 + scale_colour_ggpalette_d(direction = -1)
```

Used for fill aesthetics in ggplot2
```{r warning=FALSE}
p2 <- ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.6) +
  scale_fill_ggpalette_d() +
  theme_bw()
p2
```

Use direction = -1 to reserve the order of the palette

```{rwarning=FALSE}
p3 <- ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.6) +
  scale_fill_ggpalette_d(direction = -1) +
  theme_bw()
p3
```


